Measuring Perceptions and Preferences for Meritocracy

### 2020-07-30 docs/paper.tex
likert, corplot, tablefit, sempath, bib, preanalisis

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Measuring Perceptions and Preferences for Meritocracy},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=0.78in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{caption}
\captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

\title{Measuring Perceptions and Preferences for Meritocracy}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\setstretch{1.5}
\emph{Abstract}

Economic and social inequality have raised growing concerns and crises
across societies. One of social science concepts associated to the
maintenance of inequality is the belief in meritocracy, which would
legitimize economic differences based on effort and talent. Despite its
wide use, empirical research on meritocracy is something relatively
novel. A number of studies have relied mostly in secondary data to
operationalize meritocracy, with a large variation in the use and
interpretation of survey items. Starting from a review of studies that
measure meritocracy, this article identifies a series of drawbacks and
inconsistencies within and between studies regarding the
conceptualization and measurement of meritocracy. Based on this critical
analysis, we propose an items battery called ``Perceptions and
preferences for meritocracy scale'', which is tested with confirmatory
factor analysis with data from an online survey study (N=2,141). The
results support the proposed conceptual structure which not only
distinguishes between perceptions and preferences, but also between
meritocratic and non-meritocratic dimensions. The discussion highlights
the relevance of considering these different dimensions in order to
advance in the study of meritocracy.

\hypertarget{introducciuxf3n}{%
\section{Introducción}\label{introducciuxf3n}}

@@

\hypertarget{the-black-box-of-meritocratic-beliefs}{%
\subsection{The black-box of meritocratic
beliefs}\label{the-black-box-of-meritocratic-beliefs}}

@@

\hypertarget{an-instrument-proposal}{%
\subsection{An instrument proposal}\label{an-instrument-proposal}}

@@

The proposed measurement framework is depicted in Figure 1:

\includegraphics[width=0.6\textwidth,height=\textheight]{../input/images/generalf.png}

@@

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

@@

The proposed scale of perceptions and preferences about meritocracy
consists of 8 indicators that are grouped into the 4 dimensions referred
above: Perceptions (meritocratic/non-meritocratic) and preferences
(meritocratic/non-meritocratic). In order to achieve at least some
comparability with previous studies, the questions were adapted from the
items battery ``reasons to get ahead'' (ISSP/GSS), which are mostly used
for operationalizing meritocracy in previous empirical studies (Mijs
\protect\hyperlink{ref-mijs_paradox_2019}{2019}; Duru-Bellat and Tenret
\protect\hyperlink{ref-duru-bellat_whos_2012}{2012}; Reynolds and Xian
\protect\hyperlink{ref-reynolds_perceptions_2014}{2014}). The eight
items ordered according to dimensions are presented in Table 2. These 8
likert-type items have 5 response alternatives ranging from ``Completely
disagree''(1) to ``Completely agree'' (5).

@@

\caption{\label{tab:unnamed-chunk-6}Items according to dimension.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{14}{16}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{2 cm}>{\raggedright}X>{\raggedright}X}
\toprule
Dimension & Factor & Statement (english) & Statement (spanish)\\
\midrule
 &  & Those who try harder get greater rewards than those who work less. & Quienes más se esfuerzan logran obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent achieve greater rewards than those who have less talent. & Quienes poseen más talento logran obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & Those who have rich parents succeed. & Quienes tienen padres ricos logran salir adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Perception} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & Those who have good contacts succeed. & Quienes tienen buenos contactos logran salir adelante.\\
\cmidrule{1-4}
 &  & Those who try harder should get greater rewards than those who work less. & Quienes más se esfuerzan deberían obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent should get greater rewards than those who have less talent. & Quienes poseen más talento deberían obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & It's fine that those with rich parents get ahead. & Está bien que quienes tienen padres ricos salgan adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Preference} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & It's fine that those who have good contacts get ahead. & Está bien que quienes tienen buenos contactos salgan adelante.\\
\bottomrule
\end{tabu}}
\end{table}

@@

With the objective of evaluating the effect of the indicators ordering,
the respondents (\emph{n = 2141}) were randomly divided into three
different order versions as explained in \textbf{Figure 1}. The scale
was presented to the first group (\emph{n = 712}) in the order that
appears in Table 2. For the second group (\emph{n = 717}), the order of
the items was organized according to the topics of the items, e.g.~for
the topic of hard work the item about perception was followed by the
item about preference, and te same for the rest of the topics. Finally,
for the third group (\emph{n = 712}) the items were completely
randomized.

\begin{figure}
\centering
\includegraphics[width=0.8\textwidth,height=\textheight]{../input/images/app_mod.png}
\caption{Survey flow}
\end{figure}

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

@@

\begin{figure}
\centering
\includegraphics{../output/images/meas01.png}
\caption{Theorical model}
\end{figure}

@@

Como puede observarse en la tabla 3, los indicadores poseen valores que
van desde el 1 (totalmente en desacuerdo) al 5 (totalmente de acuerdo).
Se observan promedios desde 2.41 correspondiente a
preferencia-contactos, hasta 3.89 correspondiente a la
preferencia-esfuerzo. Ambos indicadores son coherentes con la adhesión
general a la meritocracia, privilegiando aspectos individuales como el
esfuerzo.

\begin{table}

\caption{\label{tab:unnamed-chunk-10}Descriptive statistics of the scale.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{lllll}
\toprule
  & Mean & SD & Min & Max\\
\midrule
A.Perception Effort & 3.20 & 1.38 & 1 & 5\\
B.Perception Talent & 3.02 & 1.16 & 1 & 5\\
C.Perception rich parents & 3.66 & 1.36 & 1 & 5\\
D.Perception contacts & 3.79 & 1.24 & 1 & 5\\
E.Preferences Effort & 3.89 & 1.25 & 1 & 5\\
F.Preferences Talent & 3.24 & 1.19 & 1 & 5\\
G.Preferences rich parents & 2.69 & 1.18 & 1 & 5\\
H.Preferences contacts & 2.41 & 1.11 & 1 & 5\\
\bottomrule
\end{tabular}
\end{table}

El gráfico XX muestra \ldots{} A partir del gráfico se observa que en
general hay una mayor percepción de elementos no meritocráticos que
meritocráticos, mientras que en el caso de preferencias ocurre lo
opuesto. En cuanto a las preferencias, llama la atención el rol
preponderante del esfuerzo por sobre el talento.

\begin{figure}
\centering
\includegraphics[width=11\textwidth,height=\textheight]{../output/images/plotlikert.png}
\caption{Descriptive plot}
\end{figure}

El Grafico XX muestra \ldots. Se observan relaciones de moderada a alta
intensidad entre los indicadores que corresponden al mismo factor (por
ejemplo, percepción de meritocracia esfuerzo con talento r=0.56),
mientras que se observan correlaciones de baja intensidad entre el resto
de los cruces. Destacan además las relaciones entre las percepciones y
preferencias de tipo meritocráticas, lo que no ocurre con los
indicadores no meritocraticos.

\begin{figure}
\centering
\includegraphics[width=0.9\textwidth,height=\textheight]{../output/images/corpoly.png}
\caption{polychoric correlation plot}
\end{figure}

@@

Los modelos confirmatorios fueron estimados en primer lugar para cada
uno de los tres administration-sets. Los resultados se presentan en la
Tabla XX

@@

\caption{\label{tab:unnamed-chunk-14}Factor loads and model fit.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{9}{11}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{12}{c}{Factor loadings} \\
\cmidrule(l{3pt}r{3pt}){2-13}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Version 1} & \multicolumn{4}{c}{Version 2} & \multicolumn{4}{c}{Version 3} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
Variables & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
\midrule
Perception Effort & 0.69 &  &  &  & 0.76 &  &  &  & 0.70 &  &  & \\
Perception Talent & 0.81 &  &  &  & 0.72 &  &  &  & 0.65 &  &  & \\
Perception rich parents &  & 0.85 &  &  &  & 0.84 &  &  &  & 0.81 &  & \\
Perception contacts &  & 0.94 &  &  &  & 0.81 &  &  &  & 0.89 &  & \\
Preferences Effort &  &  & 0.85 &  &  &  & 0.82 &  &  &  & 0.66 & \\
Preferences Talent &  &  & 0.64 &  &  &  & 0.65 &  &  &  & 0.59 & \\
Preferences rich parents &  &  &  & 0.55 &  &  &  & 1.04 &  &  &  & 0.78\\
Preferences contacts &  &  &  & 1.26 &  &  &  & 0.52 &  &  &  & 0.77\\
\hline
\hspace{1em}$\chi^2\text{(df)}$ &  & 42.3(14) &  &  &  & 107.6(14) &  &  &  & 63.3(14) &  & \\
\hspace{1em}$\text{CFI}$ &  & 0.993 &  &  &  & 0.961 &  &  &  & 0.979 &  & \\
\hspace{1em}$\text{RMSEA}$ &  & 0.053 &  &  &  & 0.097 &  &  &  & 0.070 &  & \\
\hspace{1em}$N$ &  & 712 &  &  &  & 717 &  &  &  & 712 &  & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Standardised factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

@@

\hypertarget{anexos}{%
\section{Anexos}\label{anexos}}

\begin{longtable}[]{@{}lcc@{}}
\caption{Representativeness of the sample.}\tabularnewline
\toprule
& Sample & CEP\tabularnewline
\midrule
\endfirsthead
\toprule
& Sample & CEP\tabularnewline
\midrule
\endhead
\textbf{gender} & &\tabularnewline
Men & 49,82\% & 50,52\%\tabularnewline
Women & 50.18\% & 49,47\%\tabularnewline
\textbf{Age} & &\tabularnewline
18 - 24 & 18,55\% & 18,17\%\tabularnewline
25 - 34 & 18,86\% & 17,48\%\tabularnewline
35 - 44 & 19.09\% & 19,98\%\tabularnewline
45 - 54 & 17,96\% & 19,23\%\tabularnewline
55 - or more & 25,54\% & 25.11\%\tabularnewline
\textbf{Education} & &\tabularnewline
Primary or less & 2,93\% & 15,88\%\tabularnewline
Hig school & 43,23\% & 37,04\%\tabularnewline
Non university & 32,63\% & 28,93\%\tabularnewline
university or more & 21,21\% & 18,13\%\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{bibliografuxeda}{%
\section*{Bibliografía}\label{bibliografuxeda}}
\addcontentsline{toc}{section}{Bibliografía}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Measuring Perceptions and Preferences for Meritocracy},
  pdfauthor={Juan Carlos Castillo, Julio Iturra \& Francisco Meneses},
  colorlinks=true,
  linkcolor=blue,
  filecolor=Maroon,
  citecolor=Blue,
  urlcolor=Blue,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=0.78in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{times}
\usepackage{caption}
\captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
\usepackage{graphicx}
\usepackage{float}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

\title{Measuring Perceptions and Preferences for Meritocracy}
\author{Juan Carlos Castillo, Julio Iturra \& Francisco Meneses}
\date{}

\begin{document}
\maketitle
\begin{abstract}
Economic and social inequality have raised growing concerns and crises across societies. One of social science concepts associated to the maintenance of inequality is the belief in meritocracy, which would legitimize economic differences based on effort and talent. Despite its wide use, empirical research on meritocracy is something relatively novel. A number of studies have relied mostly in secondary data to operationalize meritocracy, with a large variation in the use and interpretation of survey items. Starting from a review of studies that measure meritocracy, this article identifies a series of drawbacks and inconsistencies within and between studies regarding the conceptualization and measurement of meritocracy. Based on this critical analysis, we propose an items battery called \emph{Perceptions and preferences for meritocracy scale}, which is tested with confirmatory factor analysis with data from an online survey study (N=2,141). The results support the proposed conceptual structure which not only distinguishes between perceptions and preferences, but also between meritocratic and non-meritocratic dimensions. The discussion highlights the relevance of considering these different dimensions in order to advance in the study of meritocracy.
\end{abstract}

\setstretch{1.5}
\hypertarget{part-introducciuxf3n}{%
\part*{Introducción}\label{part-introducciuxf3n}}
\addcontentsline{toc}{part}{Introducción}

@@

\hypertarget{blackbox}{%
\subsection*{The black-box of meritocratic beliefs}\label{blackbox}}
\addcontentsline{toc}{subsection}{The black-box of meritocratic beliefs}

@@

\hypertarget{instrumentprop}{%
\subsection*{An instrument proposal}\label{instrumentprop}}
\addcontentsline{toc}{subsection}{An instrument proposal}

@@

The proposed measurement framework is depicted in Figure \ref{fig:merit-model}:

\begin{figure}[H]

{\centering \includegraphics[width=0.75\linewidth]{../input/images/generalf}

}

\caption{Model of perception and preferences for meritocracy and non-meritocracy}\label{fig:merit-model}
\end{figure}

@@

\hypertarget{data}{%
\subsection*{Data collection}\label{data}}
\addcontentsline{toc}{subsection}{Data collection}

@@

The proposed scale of perceptions and preferences about meritocracy consists of 8 indicators that are grouped into the 4 dimensions referred above: Perceptions (meritocratic/non-meritocratic) and preferences (meritocratic/non-meritocratic). In order to achieve at least some comparability with previous studies, the questions were adapted from the items battery ``reasons to get ahead'' (ISSP/GSS), which are mostly used for operationalizing meritocracy in previous empirical studies (Mijs \protect\hyperlink{ref-mijs_paradox_2019}{2019}; Duru-Bellat and Tenret \protect\hyperlink{ref-duru-bellat_whos_2012}{2012}; Reynolds and Xian \protect\hyperlink{ref-reynolds_perceptions_2014}{2014}). The eight items ordered according to dimensions are presented in Table \ref{tab:table-indicadores}. These 8 likert-type items have 5 response alternatives ranging from ``Completely disagree''(1) to ``Completely agree'' (5).

@@

\caption{\label{tab:table-indicadores}Items according to dimension.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{10}{12}\selectfont
\begin{tabu} to \linewidth {>{\raggedright\arraybackslash}p{1.5cm}>{\raggedright\arraybackslash}p{2 cm}>{\raggedright}X>{\raggedright}X}
\toprule
Dimension & Factor & Statement (english) & Statement (spanish)\\
\midrule
 &  & Those who try harder get greater rewards than those who work less. & Quienes más se esfuerzan logran obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent achieve greater rewards than those who have less talent. & Quienes poseen más talento logran obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & Those who have rich parents succeed. & Quienes tienen padres ricos logran salir adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Perception} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & Those who have good contacts succeed. & Quienes tienen buenos contactos logran salir adelante.\\
\cmidrule{1-4}
 &  & Those who try harder should get greater rewards than those who work less. & Quienes más se esfuerzan deberían obtener mayores recompensas que quienes se esfuerzan menos.\\
\cmidrule{3-4}
 & \multirow{-2}{2 cm}{\raggedright\arraybackslash Meritocratic} & Those who have more talent should get greater rewards than those who have less talent. & Quienes poseen más talento deberían obtener mayores recompensas que quienes poseen menos talento.\\
\cmidrule{2-4}
 &  & It's fine that those with rich parents get ahead. & Está bien que quienes tienen padres ricos salgan adelante.\\
\cmidrule{3-4}
\multirow{-4}{1.5cm}{\raggedright\arraybackslash Preference} & \multirow{-2}{2 cm}{\raggedright\arraybackslash Non meritocratic} & It's fine that those who have good contacts get ahead. & Está bien que quienes tienen buenos contactos salgan adelante.\\
\bottomrule
\end{tabu}}
\end{table}

@@

With the objective of evaluating the effect of the indicators ordering, the respondents (\emph{n = 2141}) were randomly divided into three different order versions as explained in Figure \ref{fig:appmod} . The scale was presented to the first group (\emph{n = 712}) in the order that appears in Table 2. For the second group (\emph{n = 717}), the order of the items was organized according to the topics of the items, e.g.~for the topic of hard work the item about perception was followed by the item about preference, and te same for the rest of the topics. Finally, for the third group (\emph{n = 712}) the items were completely randomized.

\begin{figure}[H]

{\centering \includegraphics[width=0.75\linewidth]{../input/images/app_mod}

}

\caption{Survey flow}\label{fig:appmod}
\end{figure}

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\begin{figure}[H]

{\centering \includegraphics[width=0.75\linewidth]{../output/images/meas01}

}

\caption{Theorical model}\label{fig:meas01}
\end{figure}

@@

Como puede observarse en la tabla \ref{tab:desc01}, los indicadores poseen valores que van desde el 1 (totalmente en desacuerdo) al 5 (totalmente de acuerdo). Se observan promedios desde 2.41 correspondiente a preferencia-contactos, hasta 3.89 correspondiente a la preferencia-esfuerzo. Ambos indicadores son coherentes con la adhesión general a la meritocracia, privilegiando aspectos individuales como el esfuerzo.

\caption{\label{tab:desc01}Descriptive statistics of the scale.}
\centering
\fontsize{10}{12}\selectfont
\begin{tabular}[t]{lllll}
\toprule
  & Mean & SD & Min & Max\\
\midrule
A.Perception Effort & 3.20 & 1.38 & 1 & 5\\
B.Perception Talent & 3.02 & 1.16 & 1 & 5\\
C.Perception rich parents & 3.66 & 1.36 & 1 & 5\\
D.Perception contacts & 3.79 & 1.24 & 1 & 5\\
E.Preferences Effort & 3.89 & 1.25 & 1 & 5\\
F.Preferences Talent & 3.24 & 1.19 & 1 & 5\\
G.Preferences rich parents & 2.69 & 1.18 & 1 & 5\\
H.Preferences contacts & 2.41 & 1.11 & 1 & 5\\
\bottomrule
\end{tabular}
\end{table}

El gráfico XX muestra \ldots{}
A partir del la Figura \ref{fig:plotlikert} se observa que en general hay una mayor percepción de elementos no meritocráticos que meritocráticos, mientras que en el caso de preferencias ocurre lo opuesto. En cuanto a las preferencias, llama la atención el rol preponderante del esfuerzo por sobre el talento.

\begin{figure}[H]

{\centering \includegraphics[width=0.75\linewidth]{../output/images/plotlikert}

}

\caption{Descriptive plot}\label{fig:plotlikert}
\end{figure}

El Grafico \ref{fig:corpoly} muestra \ldots.
Se observan relaciones de moderada a alta intensidad entre los indicadores que corresponden al mismo factor (por ejemplo, percepción de meritocracia esfuerzo con talento r=0.56), mientras que se observan correlaciones de baja intensidad entre el resto de los cruces. Destacan además las relaciones entre las percepciones y preferencias de tipo meritocráticas, lo que no ocurre con los indicadores no meritocraticos.

\begin{figure}[H]

{\centering \includegraphics[width=0.75\linewidth]{../output/images/corpoly}

}

\caption{Polychoric correlation plot}\label{fig:corpoly}
\end{figure}

@@

\begin{quote}
Julio: Esta sección debe ser revisada:
\end{quote}

\begin{itemize}
\tightlist
\item
  CFA general
\item
  Fit x modelo
\end{itemize}

{[}Aquí SEM plot con cargas y ajuste global del modelo{]}

Los modelos confirmatorios fueron estimados en primer lugar para cada uno de los tres administration-sets. Los resultados se presentan en la Tabla \ref{tab:tab-loads}

@@

\caption{\label{tab:tab-loads}Factor loads and model fit.}
\centering
\resizebox{\linewidth}{!}{
\fontsize{9}{11}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{12}{c}{Factor loadings} \\
\cmidrule(l{3pt}r{3pt}){2-13}
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Version 1} & \multicolumn{4}{c}{Version 2} & \multicolumn{4}{c}{Version 3} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9} \cmidrule(l{3pt}r{3pt}){10-13}
Variables & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4 & 1 & 2 & 3 & 4\\
\midrule
Perception Effort & 0.69 &  &  &  & 0.76 &  &  &  & 0.70 &  &  & \\
Perception Talent & 0.81 &  &  &  & 0.72 &  &  &  & 0.65 &  &  & \\
Perception rich parents &  & 0.85 &  &  &  & 0.84 &  &  &  & 0.81 &  & \\
Perception contacts &  & 0.94 &  &  &  & 0.81 &  &  &  & 0.89 &  & \\
Preferences Effort &  &  & 0.85 &  &  &  & 0.82 &  &  &  & 0.66 & \\
Preferences Talent &  &  & 0.64 &  &  &  & 0.65 &  &  &  & 0.59 & \\
Preferences rich parents &  &  &  & 0.55 &  &  &  & 1.04 &  &  &  & 0.78\\
Preferences contacts &  &  &  & 1.26 &  &  &  & 0.52 &  &  &  & 0.77\\
\hline
\hspace{1em}$\chi^2\text{(df)}$ &  & 42.3(14) &  &  &  & 107.6(14) &  &  &  & 63.3(14) &  & \\
\hspace{1em}$\text{CFI}$ &  & 0.993 &  &  &  & 0.961 &  &  &  & 0.979 &  & \\
\hspace{1em}$\text{RMSEA}$ &  & 0.053 &  &  &  & 0.097 &  &  &  & 0.070 &  & \\
\hspace{1em}$N$ &  & 712 &  &  &  & 717 &  &  &  & 712 &  & \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Note: } 
\item Standardized factor loadings using DWLS estimator ; CFI = Comparative fit index (scaled); RMSEA = Root mean square error of approximation (scaled)
\end{tablenotes}
\end{threeparttable}}
\end{table}

@@

\begin{quote}
Julio: ¿Esto se debe mantener?
\end{quote}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\begin{longtable}[]{@{}lcc@{}}
\caption{Representativeness of the sample.}\tabularnewline
\toprule
& Sample & CEP\tabularnewline
\midrule
\endfirsthead
\toprule
& Sample & CEP\tabularnewline
\midrule
\endhead
\textbf{Gender} & &\tabularnewline
Men & 49,82\% & 50,52\%\tabularnewline
Women & 50.18\% & 49,47\%\tabularnewline
\textbf{Age} & &\tabularnewline
18 - 24 & 18,55\% & 18,17\%\tabularnewline
25 - 34 & 18,86\% & 17,48\%\tabularnewline
35 - 44 & 19.09\% & 19,98\%\tabularnewline
45 - 54 & 17,96\% & 19,23\%\tabularnewline
55 - or more & 25,54\% & 25.11\%\tabularnewline
\textbf{Education} & &\tabularnewline
Primary or less & 2,93\% & 15,88\%\tabularnewline
Hig school & 43,23\% & 37,04\%\tabularnewline
Non university & 32,63\% & 28,93\%\tabularnewline
university or more & 21,21\% & 18,13\%\tabularnewline
\bottomrule
\end{longtable}
